Format for lefse and run on the classes CR and tox

### 2019-10-28 scripts/03_lefse_CR_tox.Rmd
update

Now we have 3 subclasses and together with the 2 classes of 35 that gonna make a total combination of 6

@@

```{r}
# loading the table with the valid sampleids
valid_s <- read_table('../data/input_for_cluster_sampleid/valid_sample_names.txt', col_names = F)

pheno <- read_csv('../data/cleaned_pheno/current_pheno.csv') %>% 
  filter(Sampleid %in% valid_s$X1) %>% 
  select(-Censor_YN, -Censor_reason ) 
```

@@

```{r}
# get different combination of the classes
classes <- c('CR', 'Toxicity')
subclass <- c('Disease_Status_CAR','Disease_Class','CAR_Group')

@@

```{r}
# create the commad in df with str_glue and then output to a bash script
pheno_combi <- data_frame(pheno_file = list.files('../data/lefse_input', pattern = '.txt$', full.names = T)) %>% 
  mutate(combi = str_extract(pheno_file, 'pheno.+\\.'))

pheno_combi %>% 
  mutate(cat_cmd = str_glue('cat {pheno_file} ../data/pheno_aligned_relab_table/humann2_pathabundance_relab_unstratified.tsv > ../data/lefse_input/pathway_abundace_{combi}tsv')) %>% 
  select(cat_cmd) %>% 
  write_csv('cat_combi_6.sh', col_names = F)
```

```{r}
# create the cmd to do the format input stuff
pheno_combi %>% 
  mutate(input_tsv = str_glue('../data/lefse_input/pathway_abundace_{combi}tsv'),
         fmt_input = str_replace(input_tsv, 'tsv','in'),
         fmt_cmd = str_glue('format_input.py {input_tsv} {fmt_input} -c 1 -s 2 -u 3 -o 1000000')) %>% 
  select(fmt_cmd) %>% 
  write_csv('format_input_6.sh', col_names = F)
```

```{r}
# the actual step to run lefse
pheno_combi %>% 
  mutate(fmt_input = str_glue('../data/lefse_input/pathway_abundace_{combi}in'),
         lefse_res = str_replace(fmt_input, 'in$','res'),
         run_cmd = str_glue('run_lefse.py {fmt_input} {lefse_res}')) %>% 
  select(run_cmd) %>% 
  write_csv('run_lefse.sh', col_names = F)
```

```{r}
# plotting cmd 
pheno_combi %>% 
  mutate(lefse_res = str_glue('../data/lefse_input/pathway_abundace_{combi}res'),
         fea_png = str_glue('../figs/pathway_abundace_{combi}png'),
         cmd = str_glue('plot_res.py {lefse_res}  {fea_png} --feature_font_size 4 --width 10 --dpi 300 --title {combi}')) %>% 
  select(cmd) %>% 
  write_csv('plotting_de_feature.sh', col_names = F)
```

@@

```{bash}
# this is the bash script to do the actual concatenation 
bash cat_combi_6.sh
```

```{bash}
# run in the cmd line THIS HAS TO BE DONE IN THE CMD SINCE RSTUDIO DOES NOT RECOGNIZE THE LEFSE SCRIPT
bash format_input_6.sh
```

```{bash}
bash run_lefse.sh
```

```{bash}
bash plotting_de_feature.sh
```

>>>>

@@

```{r}
pheno <- read_csv('../data/cleaned_pheno/final_pheno.csv') %>% 
  select(-CAR_Group, -Censor_reason ) 
```

@@

```{r}
# get different combination of the classes
classes <- c('CR', 'Toxicity')
subclass <- c('Disease_Class')

@@

```{r}
# create the commad in df with str_glue and then output to a bash script
pheno_combi <- tibble(pheno_file = list.files('../data/lefse_input', pattern = '.txt$', full.names = T)) %>% 
  mutate(combi = str_extract(pheno_file, 'pheno.+\\.'))

pheno_combi %>% 
  mutate(cat_cmd = str_glue('cat {pheno_file} ../data/pheno_aligned_relab_table/humann2_pathabundance_relab_unstratified.tsv > ../data/lefse_input/pathway_abundace_{combi}tsv')) %>% 
  select(cat_cmd) %>% 
  write_csv('cat_combi_CT.sh', col_names = F)
```

```{r}
# create the cmd to do the format input stuff
pheno_combi %>% 
  mutate(input_tsv = str_glue('../data/lefse_input/pathway_abundace_{combi}tsv'),
         fmt_input = str_replace(input_tsv, 'tsv','in'),
         fmt_cmd = str_glue('format_input.py {input_tsv} {fmt_input} -c 1 -s 2 -u 3 -o 1000000')) %>% 
  select(fmt_cmd) %>% 
  write_csv('format_input_CT.sh', col_names = F)
```

```{r}
# the actual step to run lefse
pheno_combi %>% 
  mutate(fmt_input = str_glue('../data/lefse_input/pathway_abundace_{combi}in'),
         lefse_res = str_replace(fmt_input, 'in$','res'),
         run_cmd = str_glue('run_lefse.py {fmt_input} {lefse_res}')) %>% 
  select(run_cmd) %>% 
  write_csv('run_lefse_CT.sh', col_names = F)
```

```{r}
# plotting cmd 
pheno_combi %>% 
  mutate(lefse_res = str_glue('../data/lefse_input/pathway_abundace_{combi}res'),
         fea_png = str_glue('../figs/pathway_abundace_{combi}png'),
         cmd = str_glue('plot_res.py {lefse_res}  {fea_png} --feature_font_size 4 --width 10 --dpi 300 --title {combi}')) %>% 
  select(cmd) %>% 
  write_csv('plotting_de_feature_CT.sh', col_names = F)
```

@@

```{bash}
# this is the bash script to do the actual concatenation 
bash cat_combi_CT.sh
bash format_input_CT.sh
bash run_lefse_CT.sh
bash plotting_de_feature_CT.sh
```
